---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=FALSE)
```

# jamesdemo

The `jamesdemo` package contains a simple Shiny app that shows site functionality of the **Joint Automatic Measurement and Evaluation System (JAMES)**. The API endpoint `request_site` as defined by [james](https://github.com/growthcharts/james) returns an URL that points to a site with personalised child charts. The `jamesdemo` app shows the site for a set of demo children. The [jamesdemodata](https://github.com/growthcharts/jamesdemodata) package stores the data of these children.

## Installation

The following statements will install the `jamesdemo` package

```{r eval = FALSE}
install.packages("remotes")
remotes::install_github("growthcharts/jamesdemo")
```

## Example

Within RStudio, view the website locally as follows:

```{r}
library(jamesdemo)
go()
```

The app does not run in the internal RStudio viewer. Click on button `Open in browser` to see it in action.

## Online version

You can spare yourself the trouble of installing the package, and visit 
`JAMES tryout` at <https://tnochildhealthstatistics.shinyapps.io/james_tryout/>.

## Resources

- [james](https://github.com/growthcharts/james)
- [jamesdemodata](https://github.com/growthcharts/jamesdemodata)
